Cluster Paper

### 2015-03-30 ms.tex
clean up preamble

%\documentclass[10pt,preprint]{aastex}
%\documentclass[iop]{emulateapj} \font\sevenrm=cmr7  \usepackage{apjfonts}
%preprint2 produces a double-column, single-spaced document:
%\documentclass[preprint2]{aastex}
\documentclass[apj, twocolappendix]{emulateapj}

\usepackage{epsf}
\usepackage{color}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{appendix}
\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{threeparttable}
\usepackage{multirow}
\usepackage{natbib}
\usepackage{etoolbox}

\bibliographystyle{apj}
\citestyle{aa}

@@

\begin{abstract}
\noindent
%
We propose to use the Mitchell Spectrograph to provide accurate mass determinations of 10
massive galaxy clusters at z=0.2-0.3 using integral field spectroscopy of the cluster galaxies.
These clusters are selected optically from the SDSS DR8, and are representative of the hundreds
of thousands of clusters expected from DES and LSST. The cluster counts provide a powerful
measure of cosmological parameters independent of supernovae and the CMB. The dominant
sources of error on these cosmological parameters from counts of optical clusters are systematic
uncertainties on the absolute scale between the cluster mass and optical richness, and the intrinsic
scatter in cluster mass at fixed richness. Here we propose a pilot study using these 10 massive
cluster to measure independently the absolute mass scale and scatter in the cluster-optical richness
relation. We will target each galaxy cluster with 4 pointings with the Mitchell Spectrograph,
obtaining integral field spectroscopy for all the (more than 100) cluster galaxies out to radii of
0.5 Mpc and luminosities down to 0.2 L*. The redshifts will allow us to calculate the line-ofsight
velocity dispersion for each cluster, which is an estimator of the total virial mass, and
calculate the precise cluster center. Using the independent cluster mass estimator from the
velocity dispersions will calibrate the mass-optical richness relation, and can lead to a decrease
on the error bars of key cosmological parameters by as much as 50\%.
%
\end{abstract}

>>>>

\documentclass[apj, revtex4]{emulateapj}

\usepackage{epsf}
\usepackage{color}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{threeparttable}
\usepackage{multirow}
\usepackage{natbib}
\usepackage{etoolbox}

\pdfoutput=1
\bibliographystyle{apj}
\citestyle{aa}

@@

\begin{abstract}
\noindent
ABSTRACT GOES HERE!!
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Cras malesuada, ante eu scelerisque gravida, augue lacus ullamcorper metus, ac volutpat libero magna rutrum nisi. Interdum et malesuada fames ac ante ipsum primis in faucibus. Ut eget magna est. Nam quis maximus purus, feugiat facilisis lectus. Nulla mollis sodales felis a ullamcorper. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur rhoncus, ligula vel venenatis ornare, nisi massa sagittis orci, in hendrerit purus libero id mauris. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos.
\end{abstract}
